Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-08 content/background.tex
decreasing figure sizes

The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\Lambda),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\Lambda),\,(n_1,\,d_1))\,.
\end{align}

>>>>

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each inter-procedurally realizable path
\[
  p=\left[(\startmain,\,\Lambda),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\Lambda),\,(n_1,\,d_1))\,.
\end{align}

### 2014-12-08 content/intro.tex
decreasing figure sizes

\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem] (ifds) {IFDS problem};
    \node [problem] (equiv) [above right=0.9cm and .7\dist of ifds.east] {Equivalent IDE problem};
    \node [problem] (ccide)[below=3cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result] (ccres) [below=3cm of equivres.west,anchor=west] {Correlated-calls result};
    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
    \path[->] (ccres) edge[out=30,in=240] node[above] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=40,in=190] node[above] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-60,in=165] node[above] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above]{$\result$} (equivres);
    \path[->] (ccide) edge node[above]{$\result$} (ccres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}

>>>>

\begin{figure}
  \centering
    \tikzset{
  ashadow/.style={opacity=.25, shadow xshift=0.07, shadow yshift=-0.07},
}
  \tikzstyle{problem}=[fill=greyblue,text width=2.3cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
  \tikzstyle{result}=[fill=bisque,text width=1.8cm,rounded corners,font=\small,text=charcoal,drop shadow={ashadow, color=greyblue}]
\begin{tikzpicture}
    \node [problem] (ifds) {IFDS problem};
    \node [problem] (equiv) [above right=0.3cm and .7\dist of ifds.east] {Equivalent IDE problem};
    \node [problem] (ccide)[below=1.6cm of equiv.west, anchor=west] {Correlated-calls IDE problem};
    \node [result] (equivres) [right=\dist of equiv.east] {Equivalence-IDE result};
    \node [result] (ccres) [below=1.6cm of equivres.west,anchor=west] {Correlated-calls result};
    \node [result] (ifdsres) [right=\dist of equivres.east] {IFDS result};
    \node [result] (improved) [right=\dist of ccres.east] {Improved IFDS result};
    \path[->] (equivres) edge node[above]{$\backEq$} (ifdsres);
    \path[->] (ccres) edge node[above] {$\backCC$} (improved);
    \path[->] (ccres) edge[out=25,in=210] node[above] {$\backEq$} (ifdsres);
    \path[->] (ifds) edge[out=40,in=179] node[above] {$\transEq$} (equiv);
    \path[->] (ifds) edge[out=-40,in=173] node[below] {$\transCC$} (ccide);
    \path[->] (equiv) edge node[above]{$\result$} (equivres);
    \path[->] (ccide) edge node[above]{$\result$} (ccres);
\end{tikzpicture}
  \caption{Transformations between IFDS and IDE problems and their results}%
  \label{fig:transformations}%
\end{figure}
